Meta-analysis of the Interoceptive Accuracy Scale

### 2025-10-20 analysis/study2.qmd
Update study2.qmd

data <- rbind(
  data,
  pool_coef(with = "PHQ15_Sum", component="Mood", category = "Mood", name = "Somatic Concerns - PHQ-15",unequalrange=TRUE), 
  pool_coef(with = "PHQ9_Sum", component="Mood", category = "Mood", name = "Depression - PHQ-9", unequalrange=TRUE), 
  pool_coef(with = "BDI_Sum", component="Mood", category = "Mood", name = "Depression - BDI"), 
  pool_coef(with = "PHQ4_Depression", component="Mood", category = "Mood", name = "Depression - PHQ-4"),
  pool_coef(with = "DEP", component = "Mood", category = "Mood", name = "Depression - MFQ")
)
```

@@

data <- rbind(
  data,
  pool_coef(with = "STAIT_Mean", component="Mood", category = "Mood", name = "Anxiety (STAI-T)", unequalrange=TRUE), 
  pool_coef(with = "PHQ4_Anxiety", component="Mood", category = "Mood", name = "Anxiety (PHQ-4)"),
  pool_coef(with = "GAD7_Sum", component="Mood", category = "Mood", name = "Anxiety (GAD-7)")
)
```

@@

check_ranges("BPD")

data <- rbind(
  data,
  pool_coef(with = "BPD", component="Mood", category = "Mood", name = "Boderline Personality")
)
```

@@

data <- rbind(
  data,
  pool_coef(with = "PID5_Antagonism", component="Maladaptive", name = "Antagonism"),
  pool_coef(with = "PID5_Detachment", component="Maladaptive", name = "Detachment"), 
  pool_coef(with = "PID5_Disinhibition", component="Maladaptive", name = "Disinhibition"),
  pool_coef(with = "PID5_NegativeAffect", component="Maladaptive", name = "Negative Affect"),
  pool_coef(with = "PID5_Psychoticism", component="Maladaptive", name = "Psychoticism")
)
```

@@

data <- rbind(
  data,
  pool_coef(with = "SPQ_ConstrictedAffect", component="Schizotypic", name = "Constricted Affect"),
  pool_coef(with = "SPQ_Eccentric", component="Schizotypic", name = "Eccentric"),
  pool_coef(with = "SPQ_MagicalThinking", component="Schizotypic", name = "Magical Thinking"),
  pool_coef(with = "SPQ_NoCloseFriends", component="Schizotypic", name = "No Close Friends"),
  pool_coef(with = "SPQ_OddSpeech", component="Schizotypic", name = "Odd Speech"),
  pool_coef(with = "SPQ_Reference", component="Schizotypic", name = "Reference"),
  pool_coef(with = "SPQ_SocialAnxiety", component="Schizotypic", name = "Social Anxiety"),
  pool_coef(with = "SPQ_Suspiciousness", component="Schizotypic", name = "Suspiciousness"),
  pool_coef(with = "SPQ_UnusualPerceptions", component="Schizotypic", name = "Unusual Perceptions")
)
```

@@

data <- rbind(
  data,
  pool_coef(with = "ASQ_Imagination", component="Autistic", name = "Imagination"),
  pool_coef(with = "ASQ_LackSocialSkills", component="Autistic", name = "Lack of Social Skills"), 
  pool_coef(with = "ASQ_LowAttentionalSwitching", component="Autistic", name = "Low Attentional Switching"),
  pool_coef(with = "ASQ_Patterns", component="Autistic", name = "Patterns and Numbers"),
  pool_coef(with = "ASQ_Routine", component="Autistic", name = "Routines")
)
```

@@

p <- data |>
  mutate(sig = ifelse(p < .01, "p < .01", ifelse(p < .001, "p < .001", "N.S.")),
         dir = sign(r),
         var_Interoception = str_replace(var_Interoception, "CoughSneeze", "Cough/Sneeze"),
         var_Interoception = str_replace(var_Interoception, "HungryThirsty", "Hungry/Thirsty"),
         var_Interoception = str_replace(var_Interoception, "BruiseBlood", "Bruise/Blood sugar"),
         var_Interoception = str_replace(var_Interoception, "MusclesPain", "Muscles/Pain"),
         var_Interoception = str_replace(var_Interoception, "BreathingHeart", "Breathing/Heart"),
         var_Interoception = str_replace(var_Interoception, "UrinateDefecate", "Urinate/Defecate"),
         var_Interoception = str_replace(var_Interoception, "WindBurp", "Wind/Burp"),
         var_Interoception = fct_relevel(var_Interoception, "Original", "Hungry/Thirsty", "Bruise/Blood sugar", "Muscles/Pain", "Cough/Sneeze", "Wind/Burp", "Breathing/Heart", "Urinate/Defecate"),
         Category = fct_relevel(
           Category, "General", "Interoception"),
         Component = fct_relevel(Component, "Personality", "Demographic", "Interoception", "MAIA")) |> 
  group_by(Component) |> 
  mutate(var_Correlate = fct_reorder(var_Correlate, r, .fun=mean)) |>
  ungroup() |>
  ggplot(aes(y = var_Correlate)) +
  annotate(geom = "rect", xmin = -0.1, xmax = 0.1, ymin = -Inf, ymax=Inf, fill = "#FFF8E1") +
  annotate(geom = "rect", xmin = c(-0.3, 0.1), xmax = c(-0.1, 0.3), ymin = -Inf, ymax=Inf, fill = "#F1F8E9") +
  annotate(geom = "rect", xmin = c(-0.6, 0.3), xmax = c(-0.3, 0.6), ymin = -Inf, ymax=Inf, fill = "#E8F5E9") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  # geom_point2(aes(y=r, color = dir, alpha = sig), size = 3) +
  geom_linerange(aes(color=dir, alpha=sig, xmax=r, xmin=0), linewidth = 1) +
  geom_linerange(aes(color = dir, alpha = sig, xmin = CI_low, xmax = CI_high, linewidth = log(N))) +
  # geom_linerange(aes(color=dir, alpha=sig, ymin=0, ymax=r, group=Sample), position = position_dodge2(width = 0.7), linewidth=2.5) +
  # geom_linerange(aes(ymin = CI_low, ymax = CI_high, color = dir, alpha=sig, group=Sample), position = position_dodge2(width = 0.7),
  #                linewidth = 1) +
  facet_grid(Category ~ var_Interoception, scales = "free", space ="free", switch = "y") +
  scale_fill_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_color_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_alpha_discrete(range = c(0.2, 0.9), guide = "none") +
  scale_x_continuous(expand = c(0, 0), breaks = c(-0.3, 0, 0.3)) +
  scale_linewidth_continuous(range = c(3, 7), guide = "none") +
  coord_cartesian(xlim = c(-0.47, 0.47)) +
  theme_modern(axis.title.space = 5) +
  labs(x = "Strength of Association (std. Beta)") +
  theme(panel.grid.major.y = element_line(),
        axis.title.y = element_blank(),
        axis.line.x = element_blank(),
        axis.text.y = element_text(size = rel(0.5)),
        axis.text.x = element_text(size = rel(0.8)),
        plot.title = element_text(face = "bold", hjust = 0),
        strip.placement = "outside",
        strip.background.y = element_rect(fill = "#E0E0E0", color = "white"),
        strip.background.x = element_rect(fill = "#F8BBD0", color = "white"))
p
ggsave("figures/Figure3.png", p, width=21*1, height=29.7*1, dpi=300, bg="white")
```

>>>>

data <- rbind(
  data,
  pool_coef(with = "PHQ15_Sum", component="Depression", category = "Mood", name = "Somatic Concerns - PHQ-15",unequalrange=TRUE), 
  pool_coef(with = "PHQ9_Sum", component="Depression", category = "Mood", name = "Depression - PHQ-9", unequalrange=TRUE), 
  pool_coef(with = "BDI_Sum", component="Depression", category = "Mood", name = "Depression - BDI"), 
  pool_coef(with = "PHQ4_Depression", component="Depression", category = "Mood", name = "Depression - PHQ-4"),
  pool_coef(with = "DEP", component = "Depression", category = "Mood", name = "Depression - MFQ")
)
```

@@

data <- rbind(
  data,
  pool_coef(with = "STAIT_Mean", component="Anxiety", category = "Mood", name = "Anxiety - STAI-T", unequalrange=TRUE), 
  pool_coef(with = "PHQ4_Anxiety", component="Anxiety", category = "Mood", name = "Anxiety - PHQ-4"),
  pool_coef(with = "GAD7_Sum", component="Anxiety", category = "Mood", name = "Anxiety - GAD-7")
)
```

@@

# check_ranges("BPD")

data <- rbind(
  data,
  pool_coef(with = "BPD", component="Maladaptive", category = "Psychopathology", name = "Boderline Personality")
)
```

@@

# check_ranges("PID5_Antagonism")

data <- rbind(
  data,
  pool_coef(with = "PID5_Antagonism", component="Maladaptive", category = "Psychopathology", name = "Antagonism - PID-5"),
  pool_coef(with = "PID5_Detachment", component="Maladaptive", category = "Psychopathology", name = "Detachment - PID-5"), 
  pool_coef(with = "PID5_Disinhibition", component="Maladaptive", category = "Psychopathology", name = "Disinhibition - PID-5"),
  pool_coef(with = "PID5_NegativeAffect", component="Maladaptive", category = "Psychopathology", name = "Negative Affect - PID-5"),
  pool_coef(with = "PID5_Psychoticism", component="Maladaptive", category = "Psychopathology", name = "Psychoticism - PID-5")
)
```

@@

data <- rbind(
  data,
  pool_coef(with = "SPQ_ConstrictedAffect", component="Schizotypic", category = "Psychopathology", name = "Constricted Affect - SPQ"),
  pool_coef(with = "SPQ_Eccentric", component="Schizotypic", category = "Psychopathology", name = "Eccentric - SPQ"),
  pool_coef(with = "SPQ_MagicalThinking", component="Schizotypic", category = "Psychopathology", name = "Magical Thinking - SPQ"),
  pool_coef(with = "SPQ_NoCloseFriends", component="Schizotypic", category = "Psychopathology", name = "No Close Friends - SPQ"),
  pool_coef(with = "SPQ_OddSpeech", component="Schizotypic", category = "Psychopathology", name = "Odd Speech - SPQ"),
  pool_coef(with = "SPQ_Reference", component="Schizotypic", category = "Psychopathology", name = "Reference - SPQ"),
  pool_coef(with = "SPQ_SocialAnxiety", component="Schizotypic", category = "Psychopathology", name = "Social Anxiety - SPQ"),
  pool_coef(with = "SPQ_Suspiciousness", component="Schizotypic", category = "Psychopathology", name = "Suspiciousness - SPQ"),
  pool_coef(with = "SPQ_UnusualPerceptions", component="Schizotypic", category = "Psychopathology", name = "Unusual Perceptions - SPQ")
)
```

@@

data <- rbind(
  data,
  pool_coef(with = "ASQ_Imagination", component="Autistic", category = "Psychopathology", name = "Imagination - ASQ"),
  pool_coef(with = "ASQ_LackSocialSkills", component="Autistic", category = "Psychopathology", name = "Lack of Social Skills - ASQ"), 
  pool_coef(with = "ASQ_LowAttentionalSwitching", component="Autistic", category = "Psychopathology", name = "Low Attentional Switching - ASQ"),
  pool_coef(with = "ASQ_Patterns", component="Autistic", category = "Psychopathology", name = "Patterns and Numbers - ASQ"),
  pool_coef(with = "ASQ_Routine", component="Autistic", category = "Psychopathology", name = "Routines - ASQ")
)
```

@@

p <- data |>
  mutate(sig = ifelse(p < .01, "p < .01", ifelse(p < .001, "p < .001", "N.S.")),
         dir = sign(r),
         var_Interoception = str_replace(var_Interoception, "CoughSneeze", "Cough/Sneeze"),
         var_Interoception = str_replace(var_Interoception, "HungryThirsty", "Hungry/Thirsty"),
         var_Interoception = str_replace(var_Interoception, "BruiseBlood", "Bruise/Blood sugar"),
         var_Interoception = str_replace(var_Interoception, "MusclesPain", "Muscles/Pain"),
         var_Interoception = str_replace(var_Interoception, "BreathingHeart", "Breathing/Heart"),
         var_Interoception = str_replace(var_Interoception, "UrinateDefecate", "Urinate/Defecate"),
         var_Interoception = str_replace(var_Interoception, "WindBurp", "Wind/Burp"),
         var_Interoception = fct_relevel(var_Interoception, "Original", "Hungry/Thirsty", "Bruise/Blood sugar", "Muscles/Pain", "Cough/Sneeze", "Wind/Burp", "Breathing/Heart", "Urinate/Defecate"),
         Category = fct_relevel(
           Category, "General", "Interoception", "Mood", "Psychopathology"),
         Component = fct_relevel(Component, "Personality", "Demographic", "Interoception", "MAIA", "Anxiety", "Depression", "Schizotypic", "Autistic", "Maladaptive")) |> 
  group_by(Component) |> 
  mutate(var_Correlate = fct_reorder(var_Correlate, r, .fun=mean)) |>
  ungroup() |>
  ggplot(aes(y = var_Correlate)) +
  annotate(geom = "rect", xmin = -0.1, xmax = 0.1, ymin = -Inf, ymax=Inf, fill = "#FFF8E1") +
  annotate(geom = "rect", xmin = c(-0.3, 0.1), xmax = c(-0.1, 0.3), ymin = -Inf, ymax=Inf, fill = "#F1F8E9") +
  annotate(geom = "rect", xmin = c(-0.6, 0.3), xmax = c(-0.3, 0.6), ymin = -Inf, ymax=Inf, fill = "#E8F5E9") +
  geom_vline(xintercept = 0, linetype = "dashed") +
  # geom_point2(aes(y=r, color = dir, alpha = sig), size = 3) +
  geom_linerange(aes(color=dir, alpha=sig, xmax=r, xmin=0), linewidth = 1) +
  geom_linerange(aes(color = dir, alpha = sig, xmin = CI_low, xmax = CI_high, linewidth = log(N))) +
  # geom_linerange(aes(color=dir, alpha=sig, ymin=0, ymax=r, group=Sample), position = position_dodge2(width = 0.7), linewidth=2.5) +
  # geom_linerange(aes(ymin = CI_low, ymax = CI_high, color = dir, alpha=sig, group=Sample), position = position_dodge2(width = 0.7),
  #                linewidth = 1) +
  facet_grid(Category ~ var_Interoception, scales = "free", space ="free", switch = "y") +
  scale_fill_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_color_gradient(low = "#2196F3", high = "#FF5722", guide = "none") +
  scale_alpha_discrete(range = c(0.2, 0.9), guide = "none") +
  scale_x_continuous(expand = c(0, 0), breaks = c(-0.3, 0, 0.3)) +
  scale_linewidth_continuous(range = c(3, 7), guide = "none") +
  coord_cartesian(xlim = c(-0.47, 0.47)) +
  theme_modern(axis.title.space = 5) +
  labs(x = "Strength of Association (std. Beta)") +
  theme(panel.grid.major.y = element_line(),
        axis.title.y = element_blank(),
        axis.line.x = element_blank(),
        axis.text.y = element_text(size = rel(0.5)),
        axis.text.x = element_text(size = rel(0.8)),
        plot.title = element_text(face = "bold", hjust = 0),
        strip.placement = "outside",
        strip.background.y = element_rect(fill = "#E0E0E0", color = "white"),
        strip.background.x = element_rect(fill = "#F8BBD0", color = "white"))
p
ggsave("figures/Figure3.png", p, width=21*1, height=29.7*1, dpi=300, bg="white")
```
